%-------------------------
% Resume in Latex
% Author : Apoorv Malik
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \usepackage{xcolor}
\usepackage[usenames, dvipsnames]{xcolor}
\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    filecolor=RoyalBlue,      
    urlcolor=RoyalBlue,
    citecolor=RoyalBlue,
}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}



\begin{center}
    \textbf{\Huge \scshape Apoorv Malik} \\ \vspace{5pt}
    (541)-250-7410 $|$ \href{mailto:malikap@oregonstate.edu}{\underline{malikap@oregonstate.edu}}
\end{center}

\begin{center} 
    \href{http://apoorvmalik.com}{\underline{apoorvmalik.com}} $|$
    \href{https://linkedin.com/in/maliap}{\underline{linkedin.com/in/maliap}} $|$
    \href{https://github.com/1998apoorvmalik}{\underline{github.com/1998apoorvmalik}} $|$
    \href{https://leetcode.com/1998apoorvmalik}{\underline{leetcode.com/1998apoorvmalik}}
\end{center}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Tools}{: C, C++, C\#, Python, Haskell, Dart, HTML, CSS, JS, EJS, TensorFlow \& Keras, PyTorch, Scikit-Learn, OpenCV, Flask, Numpy, Pandas, Node, Express, nginx, jQuery, React, Three.js, Bootstrap, MongoDB, SQL, Docker, Flutter, Firebase, AWS, Unity, OpenGL, Figma, API Development, Git/GitHub, Linux/Bash } \\

     \textbf{Research \& CS Interests}{: Computational Biology (RNA Structure Prediction), Software Development (Mobile, Desktop and Web), Machine Learning, Computer Vision, Algorithms \& Theory, Computer Graphics, UI/UX }
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR, USA}
      {MS in Computer Science (GPA = 3.9)}{Sept. 2022 – Present}
    \resumeSubheading
      {Maharshi Dayanand University}{Rohtak, HR, India}
      {Bachelor of Technology (BTech) in Computer Science \& Engineering (CGPA = 9.2)}{Sept. 2016 – Sept. 2020}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Assistant (mentored by \href{https://web.engr.oregonstate.edu/~huanlian/}{\underline{Prof. Liang Huang}})}{December 2022 -- Present}
      {Dept. of Computer Science at Oregon State University}{Corvallis, OR, USA}
      \resumeItemListStart
        \resumeItem{Developed efficient and highly accurate prediction algorithms for RNA folding and RNA design.}
        \resumeItem{Developed a linear time algorithm for RNA alignments, supporting calculations for partition function, base pairing probabilities, secondary structure predictions (MFE, MEA, Threshknot), and stochastic sampling of structures.} 
        \resumeItem{Developed \href{https://linearfold.eecs.oregonstate.edu}{\underline{7 web servers}} to host various RNA algorithms, enhancing the accessibility of our scientific tools.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant (Algorithms and Theory of Computation)}{March 2023 -- Present}
      {Dept. of Computer Science at Oregon State University}{Corvallis, OR, USA}
      \resumeItemListStart
          \resumeItem{Taught key concepts in Algorithms and Theory of Computation, including Complexity Analysis, Divide \& Conquer strategies, Greedy \& Graph Algorithms, Dynamic Programming, Grammar, and Turing Machines.}
        \resumeItem{Graded assignments and exams, providing constructive feedback to over 300 students and collaborated closely with the course professor/instructor to design and modify course materials and assignments.}
        \resumeItem{Regularly held office hours to address individual student’s questions and maintained effective communication.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Development and Machine Learning Engineer}{January 2020 - August 2022}
      {Twyn (Previously Known as Marj Technologies)}{Noida, UP, India}
      \resumeItemListStart
        \resumeItem{Developed 3 IoT-based Industrial Automation and Quality Control applications for Non-Contact Dimensional \& Quality Inspection, OCR, Parameter-based PA check, Object Classification, and Bar \& QR code scanning.}
        \resumeItem{Contributed to the startup’s seed funding of \$328K and helped achieve a valuation of \$3.7M by completing 4 projects for multiple clients of Marj (Ask Fras le Friction, Minda Group, Samsung India, and JBM).}
        \resumeItem{Interviewed 30+ job applicants for AI \& Software Development positions and further built \& managed the core team of 8 developers for product development. Implemented agile development methodologies, such as Scrum, to improve team efficiency.}
        \resumeItem{Led cross-functional teams of developers to deliver software projects on time and within budget, provided mentorship to 3 junior developers to improve their skills.}
    \resumeItemListEnd


  \resumeSubHeadingListEnd


  \section{Publications/Preprints}
  \resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{\textbf{Apoorv Malik}, Liang Zhang, Ning Dai, Sizhen Li, He Zhang, David Mathews, and Liang Huang (2024). \textcolor{RoyalBlue}{LinearAlifold: Linear-Time Consensus Structure Prediction for RNA Alignments}. Journal of Molecular Biology (JMB) Special Issue on Computation Resources for Molecular Biology. \href{https://www.sciencedirect.com/science/article/pii/S0022283624002961}{(\underline{Publication Link})}}
    \resumeItem{Tianshuo Zhou, \textbf{Apoorv Malik}, Wei Yu Tang, Liang Huang. Scalable and Interpretable Identification of Minimal Undesignable RNA Structure Motifs with Rotational Invariance. To appear in RECOMB 2025. \href{https://arxiv.org/abs/2402.17206}{(\underline{arXiv Link})}}
    \resumeItem{Sizhen Li, \textbf{Apoorv Malik}, Ning Dai, He Zhang, David H. Mathews, and Liang Huang. \textcolor{RoyalBlue}{LinearSankoff: Linear-time Simultaneous Folding and Alignment of RNA Homologs}. In submission to NAR Journal. \href{https://arxiv.org/abs/2307.09580}{(\underline{arXiv Link})}}
    \resumeItem{Liang Huang, Otso Barron, \textbf{Apoorv Malik}, Sizhen Li, David H. Mathews. \textcolor{RoyalBlue}{Lazy Outside and Lazy Backward Algorithms}. ISMB 2024 (International Society for Computational Biology). }

\resumeItemListEnd
  \resumeSubHeadingListEnd
    

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Motifs} $|$ \href{https://linearfold.eecs.oregonstate.edu/motifs}{\underline{Web Server Link}} $|$ \href{https://arxiv.org/abs/2402.17206}{\underline{arXiv Link}}} {December 2024}
            \resumeItemListStart
                \resumeItem{Developed a full-stack web app to maintain database of unique minimal undesignable RNA structures and motifs.}
                \resumeItem{Users can explore, visualize, analyze, and identify undesignable motifs in existing and new RNA structures.}
                \resumeItem{Frontend built with React, backend powered by Flask and Express, with MongoDB for data storage.}
                \resumeItem{Deployed using Docker and Nginx for scalability and performance.}
            \resumeItemListEnd
            
      \resumeProjectHeading
          {\textbf{LinearAlifold} $|$ \href{https://linearfold.eecs.oregonstate.edu/linear-alifold}{\underline{Web Server Link}} $|$ \href{https://github.com/LinearFold/LinearAlifold}
          {\underline{GitHub Link}} $|$ \href{https://www.sciencedirect.com/science/article/pii/S0022283624002961}{\underline{Publication Link}}} {November 2023}
          \resumeItemListStart
            \resumeItem{ Developed a dynamic programming algorithm for RNA alignments' linear-time consensus structure prediction. It incorporates beam pruning (for enhanced computational efficiency), multiple energy parameters, and various computational modes.}
            \resumeItem{Enabled computation of the partition function and base pairing probabilities, with added support for predicting Maximum Expected Accuracy (MEA), Minimum Free Energy (MFE), and Threshknot structures. Additionally, implemented a mode for the Stochastic Sampling of Secondary Structures.}
            \resumeItem{Developed a web server for providing users the ability to input their own sequences and perform various functions, thereby enhancing practical applications of the tool. }
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Google Explore ML DSC Facilitator} $|$ \href{https://drive.google.com/file/d/15abBtBUW1hRcmjXRya3rsrgSMyHbqR-4/view}{\underline{Certificate Link}}}{April 2020}
          \resumeItemListStart
            \resumeItem{Conducted five workshops on machine learning, introducing core concepts and practical applications.}
            \resumeItem{Facilitated as part of the Google-sponsored Explore ML program, enhancing machine learning awareness among university students.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Computer Vision Project for Ask Fras-Le Friction Pvt. Ltd.}}{May 2022}
          \resumeItemListStart
            \resumeItem{Automated part of the quality control and inspection process by developing a vision-based application for dimensional analysis and classification of brake liners in an industrial setting.}
            \resumeItem{Utilized multiple vision cameras for real-time measurement and quality assessment.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Machine Learning Engineer Capstone Project} $|$ \href{https://github.com/1998apoorvmalik/machine-learning-engineer-capstone}{\underline{GitHub Link}}}{July 2019}
          \resumeItemListStart
            \resumeItem{Developed a Deep Q-Learning (Reinforcement Learning) algorithm enabling an AI agent to master and significantly beat human players in the game of Atari Breakout.}
            \resumeItem{The AI agent discovered innovative strategies for high scoring, demonstrating the effectiveness of the implemented learning techniques and algorithmic intelligence.}
          \resumeItemListEnd

       \resumeProjectHeading
          {\textbf{Chess Game Development} $|$ \href{https://1998apoorvmalik.github.io/flutter-chess/}{\underline{Demo Link}} $|$ \href{https://github.com/1998apoorvmalik/flutter-chess}{\underline{GitHub Link}}}{March 2022}
          \resumeItemListStart
            \resumeItem{Programmed a chess game from scratch in Flutter \& C++, focusing on efficient move generation using bitboards.}
            \resumeItem{Implemented advanced game features, including an AI opponent using the NegaMax algorithm and online multiplayer capabilities.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Teachable Image Classifier} $|$ \href{https://github.com/1998apoorvmalik/teachable-image-classifier}{\underline{GitHub Link}}}{January 2022}
          \resumeItemListStart
            \resumeItem{Created a app for non-experts to train deep learning models, enabling class creation and image sample addition.}
            \resumeItem{Designed with adjustable training parameters, making deep learning accessible and customizable for various needs.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Vedic Life Foundation App Development}}{September 2021}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive mobile application for meditation teaching, member enrollment, and session tracking, compatible with both iOS and Android platforms.}
            \resumeItem{Included social media features for community engagement, allowing users to share thoughts, ask questions, and track meditation progress.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{2021 Flutter Development Bootcamp} $|$ \href{https://www.udemy.com/certificate/UC-5f383487-e6d6-4b9a-a33c-cd0f8b353f5f/}{\underline{Certificate Link}}}{January 2022}
          \resumeItemListStart
            \resumeItem{Mastered Flutter and Dart for cross-platform app development, UI design, and state management techniques.}
            \resumeItem{Developed skills in API integration, Firebase services, animations, and deploying production-ready mobile apps.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Udacity - Artificial Intelligence Nanodegree} $|$ \href{https://graduation.udacity.com/confirm/CTCD9YJQ}{\underline{Certificate Link}} $|$ \href{https://github.com/1998apoorvmalik/udacity-artificial-intelligence-nanodegree}{\underline{GitHub Link}}}{June 2020}
          \resumeItemListStart
            \resumeItem{Learned AI techniques including classical search, constraint satisfaction problems, and local search optimization.}
            \resumeItem{Gained experience in adversarial search (Minimax, Monte Carlo Tree Search) and probabilistic reasoning with Hidden Markov Models.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Udacity - Machine Learning Engineer Nanodegree} $|$ \href{https://graduation.udacity.com/confirm/6S23AEJ5}{\underline{Certificate Link}} $|$ \href{https://github.com/1998apoorvmalik/udacity-machine-learning-engineer-nanodegree}{\underline{GitHub Link}}}{August 2019}
          \resumeItemListStart
            \resumeItem{Mastered supervised (Regression, KNN, Random Forest, SVM) and unsupervised learning (Clustering, GMM)}
            \resumeItem{Gained proficiency in data preprocessing, including data cleaning, normalization, feature engineering, and applied PCA for high-dimensional datasets.}
            \resumeItem{Developed expertise in Deep Learning (CNNs) for image classification and Reinforcement Learning (Q-Learning, DQN, Actor-Critic, DDPG) for autonomous decision-making in complex environments.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
%-------------------------------------------
\end{document}
